A Meta-Analysis of Music Emotion Recognition Studies

### 2025-03-19 manuscript/_figure4.qmd
updates to manuscript

#gridExtra::grid.arrange(fp1, fp2, ncol=2, widths=c(2,1))
#ggarrange(fp1,fp2, ncol = 2, labels = c("A","B"),widths=c(2,1)) # added labels A and B
ggarrange(fp1)

```

>>>>

#gridExtra::grid.arrange(fp1, fp2, ncol=2, widths=c(2,1))
#ggarrange(fp1,fp2, ncol = 2, labels = c("A","B"),widths=c(2,1)) # added labels A and B
ggarrange(fp1)
```

### 2025-03-19 manuscript/manuscript-apaquarto.qmd
updates to manuscript

{{< include _figure1.qmd >}}

@@

```{r}
#| label: tbl-table1
#| id: tbl-table1
#| output: asis
#| warning: false
#| message: false
#| tbl-cap: Summary of the models for regression and classification studies.
library(tidyverse)
library(kableExtra)

t <- tibble(Info = c("Study N","Model N","Techniques","Techniques","Techniques","Techniques","Techniques","Feature N","Stimulus N"), 
       Regression = c("22","204","Neural Nets: 64","Support Vector Machines: 62","Linear Methods: 62","Tree-based Methods: 14","KS, Add. & KNN: 2","Min=3, Md=653, Max=14460","Min=20, Md=324, Max=2486"),
       Classification = c("12","86","21","26","19","16","4","Min=6, Md=98, Max=8904","Min=124, Md=300, Max=5192"),
       Total = c("34","290","85","88","81","30","6","NA","NA")) 
print(knitr::kable(t,bookstabs=TRUE))
#  theme_apa()

@@

>>>>

![Flowchart of the study inclusions/eliminations.](figure1.svg){width="580"}

@@

```{r}
#| id: table1
#| output: asis
#| error: false
#| warning: false
#| message: false
#| tbl-cap: Summary of the models for regression and classification studies.
knitr::opts_chunk$set(warning = FALSE, message = FALSE) 
suppressPackageStartupMessages(library(tidyverse))
suppressPackageStartupMessages(library(kableExtra))
#suppressPackageStartupMessages(library(flextable))

t <- tibble(Info = c("Study N","Model N","Techniques","Techniques","Techniques","Techniques","Techniques","Feature N","Stimulus N"), 
       Regression = c("22","204","Neural Nets: 64","Support Vector Machines: 62","Linear Methods: 62","Tree-based Methods: 14","KS, Add. & KNN: 2","Min=3, Md=653, Max=14460","Min=20, Md=324, Max=2486"),
       Classification = c("12","86","21","26","19","16","4","Min=6, Md=98, Max=8904","Min=124, Md=300, Max=5192"),
       Total = c("34","290","85","88","81","30","6","NA","NA")) 
print(knitr::kable(t,bookstabs=TRUE))
#flextable(t) %>% theme_apa()

@@

{{< include _figure2.qmd >}}

{{< include _figure3.qmd >}}

{{< include _figure4.qmd >}}
